\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-12 sections/methods.tex
Change: Update the TA section of the Results

  \subsection*{Denoising and Clustering (DC)}
  \vspace{-5mm}
  This module deals with processing the quality-controlled, trimmed 16S sequence data into \ac{otu} or \ac{esv} count tables.
  It consists of the following processes: denoising (or clustering) and chimera checking.
  The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods, like closed reference and open reference clustering, perform clustering and taxonomy assignment in the same step).
  The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
  The output of this module is a matrix of counts, that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix).
  The options currently available in the pipeline for denoising and clustering are: open reference clustering, closed reference clustering and de novo clustering methods from the vsearch plugin of \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019} and denoising methods from \ac{dada2} v1.14~\cite{Callahan2016} and Deblur v1.1.0~\cite{Amir2017} (from the deblur plugin of \ac{qiime2}).
  The quality filtering and chimera checking tools are derived from those used in \ac{qiime2} v2021.8.0 (uchime method) and \ac{dada2} (remove bimera method).

>>>>

  \subsection*{Denoising and Clustering (DC)}
  \vspace{-5mm}
  This module deals with processing the quality-controlled, trimmed 16S sequence data into \ac{otu} or \ac{esv} count tables.
  It consists of the following processes: denoising (or clustering) and chimera checking.
  The denoise/cluster process handles the conversion of the demultiplexed, trimmed sequences into \ac{otu} or \ac{esv} count tables (some methods, like closed reference and open reference clustering, perform clustering and taxonomy assignment in the same step).
  The chimera checking process handles the removal of chimeric sequences created during the \ac{pcr} step.
  The output of this module is a matrix of counts, that describes the number of reads of a particular \ac{otu} or \ac{esv} (rows of the matrix) present in each sample (columns of the matrix).
  The options currently available in the pipeline for denoising and clustering are: open reference clustering, closed reference clustering and de novo clustering methods from the vsearch plugin of \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019} and denoising methods from \ac{dada2} v1.14~\cite{Callahan2016} (from the \ac{dada2} R package) and Deblur v1.1.0~\cite{Amir2017} (from the deblur plugin of \ac{qiime2}).
  The quality filtering and chimera checking tools are derived from those used in \ac{qiime2} v2021.8.0 (uchime method) and \ac{dada2} (remove bimera method).

### 2022-04-12 sections/results.tex
Change: Update the TA section of the Results

  % Main takeaway -> TA is most important
  % Talk about OP also
  % What does PCA tell us?
  % Conclusion

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are peformed only on the control samples in the FMT study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  % TODO: Verify this
  The reason for this seems to derive from the mislabelling of constitutive taxa that are present in high abundance in the community, which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

  Figure \ref{fig:figure2}B is the PCA plot of all the generated co-occurrence networks, colored by the databases in the TA step (left) and the network inference algorihtms in the NI step (right).
  In other words, each point corresponds to a network generated using different combination of tools, and captures how much the final network is affected by such choice.
  The importance of the TA step indicated in Figure \ref{fig:figure2}A is also reflected here, in the fact that most of the networks can be clearly separated based on the database used (Figure \ref{fig:figure2}B).
  However, it is also evident that some of the networks, especially those inferred using the direct association based network infernce methods, are much closer in the PCA plot regardless of the reference database used.
  % TODO: Figure out the how the OP step plays a role in the PCA plot
  It can also be seen that the dissimilarity between the networks decreases when the low abundance \ac{otu}s are removed from the network.
  These results suggest that the most important criterion for accurate comparative analyses of co-occurrence networks is the taxonomy reference database and the level of filtering of the taxonomy tables prior to network inference.

@@

  Denoising and clustering are commonly carried out to generate representative sequences from the raw 16S sequencing data and to obtain the \ac{otu}/\ac{esv} tables (counts of these representative sequences for each sample).
  In order to compare the \ac{otu} tables generated by different tools we processed the same 16S sequencing reads (healthy samples from a fecal microbiome transplant study~\cite{Kang2017}) using 5 different methods:  open-reference clustering, closed-reference clustering, denovo clustering, \ac{dada2}~\cite{Callahan2016} and Deblur~\cite{Amir2017}.
  The first three methods are from the \ac{qiime1}~\cite{Caporaso2010} package.
  We find that there is good agreement in the \ac{otu}/\ac{esv} tables when different combinations of methods are used to generate them (Supplementary Figure~\ref{fig:figureS1}).

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A one can see that the representative sequences generated by the different methods are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the treatment of sequences of low abundance.
  In order to verify this claim, for each of these methods we use the \ac{gg} taxonomy database to assign taxonomies to the representative sequences.
  We then correlate the abundances of matching taxonomies between a pair of DC methods (Figure \ref{fig:figureS1}A and B).
  The \ac{esv} tables generated by methods that perform denoising are very similar to each other ($\sim0.91$) and the \ac{otu} tables generated by the clustering methods are very similar to each other ($\sim0.9$), but results of denoising and clustering are highly uncorrelated with each other ($\sim0.4$) (Figure \ref{fig:figureS1}C).

  These comparisons only elucidate the pairwise similarity or dissimilarity of a pair of methods.
  In order to determine the tool that most accurately recapitulates the reference sequences in the samples, we used the 16S sequences from the mock datasets.
  In particular, we used the pipeline to process mock community datasets using each of the possible methods included for this step.
  We next compared predicted representative sequences with expected representative sequences and their distribution.
  The results (Figure~\ref{fig:figure3}C and D) show that, for the mock datasets, the different methods perform similar to each other, exactly as observed in the case of the real dataset. However, the mock predicted sequence distributions are substantially different from the expected sequence distribution.
  This result is more exaggerated in the case of the unweighted UniFrac metric, where some of the datasets show a very high deviation from the expected sequences.
  These high deviations are primarily in two of the three datasets that were analyzed and show that the datasets themselves play a big role in the performance of these methods.
  This can be clearly seen in the performance (weighted UniFrac distance) of \ac{dada2} and Deblur on mock12 and mock16 datasets, where, Deblur outperforms \ac{dada2} on mock12 but the under-performs on mock16.

  There is no method that clearly outperforms the rest in all datasets.
  Based on their slightly better performance on the mock datasets, their \textit{de novo} error correcting nature and other previous studies~\cite{Nearing2018}, \ac{dada2} and Deblur seem to be in general the most reliable.
  Given the unexpected poor performance of Deblur on the synthetic data, the default algorithm in the pipeline was chosen to be \ac{dada2} (Supplementary Figure~\ref{fig:figureS3}).

  % TODO: This is the most important statement (look at the dada2 paper for better arguments)
  We prefer dada2 because it peforms marginally better (value??) than the other methods and it is also performs independent of the taxonomy database (so does denovo why are you suggesting this then?).
  Denovo also performs better but the denoising helps when there are more sequences (where is the proof?) [ref]

@@

  Taxonomy databases are used to assign taxonomic identities to the representative sequences obtained after the DC step.
  In order to compare the assigned taxonomies from different databases, we use the same reference sequences and assign taxonomies to them using different taxonomy reference databases.
  The three 16S taxonomic reference databases used in this study are SILVA~\cite{Quast2012}, \ac{gg}~\cite{DeSantis2006} and \ac{ncbi} RefSeq~\cite{Sayers2009}.
  SILVA and \ac{gg} are two popular 16S databases used for taxonomy identification.
  The \ac{ncbi} RefSeq nucleotide database contains 16S rRNA sequences as a part of two BioProjects - 33175 and 33317.
  The three databases vastly differ in terms of their last update status - \ac{gg} was last updated on May 2013, SILVA was last updated on December 2017 at the time of writing and \ac{ncbi} is updated as new sequences are curated.
  Since updates to taxonomic classifications are frequent, these databases vary significantly in terms of taxonomy hierarchies including species names and phylogenetic relationships~\cite{Balvociute2017}.

  The representative sequences obtained from the \ac{dada2} method in the DC step were used for taxonomic assignment using the three reference databases.
  Figure~\ref{fig:figure4}A depicts a flow diagram that shows how the top 50 representative sequences (sorted by abundance) are assigned a Genus according to the three different databases.
  % TOOD: Update with a more quantitative description
  We observe that not only does the assigned Genus composition vary significantly, but the percentage of unassigned representative sequences (gray) also differ.
  Even the most abundant representative sequence is assigned to an "unknown" Genus in two of the three databases.
  A representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a Genus; the second (more likely) reason is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between assignments from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<70\%$ similarity between any pair of databases.
  There are no two reference databases that are more similar than the other pairs, with \ac{gg} and SILVA producing only marginally similar assignments compared to \ac{ncbi}.
  This implies that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.

  Supplementary Figure~\ref{fig:figureS4} shows that the top 20 most abundant genera in the three resulting taxonomy composition tables are different.
  For example, the most abundant genus in the \ac{gg} taxonomy table was \textit{Escherichia} whereas in the SILVA taxonomy table it was \textit{Escherichia-Shigella}.
  Although these are minor differences, when comparing a large number of taxonomy composition tables these problems are hard to diagnose.
%   The comparison of all assigned genera instead of the just the top 20 contains the same percentage of matches and mismatches, implying that there does not seem to exist a correlation between abundance and mismatch.
%   This suggests that the most abundant sequences are not necessarily the ones that are consistently matched to the same taxonomies in the different reference databases.

  As in the previous section, these comparisons only indicate similarity or dissimilarity between methods.
  In order to obtain an absolute measure of accuracy of the taxonomic assignments we use the expected reference sequences from the mock datasets as the query sequences for the databases and the expected taxonomic composition as the standard to compare against (Figure~\ref{fig:figure4}C).
  Again, we observe that none of the databases perform better than the others in absolute terms.

  Given that no database performs better than others against mock datasets, and that databases are almost equally distant from each other in terms of final output, the choice of which database to use should be driven by other reasons.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth, which prompted us to set \ac{ncbi} as the \ac{micone} standard for taxonomy assignment.
 In addition to being regularly maintained and updated the \ac{ncbi} database already has the advantage that its accuracy of assignments is still comparable to the SILVA and \ac{gg} reference databases that are routinely used as reference databases.

 % TODO: This is the most important statement here
 From previous studies, (refer to the Bokulich2018 paper here) which have done more quantitative benchmarks on the subject of which tool is the best (for classifer)...
 There are also other studies, [ref, OTT paper] that focus on the database aspect and they too have found that...

>>>>

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are performed on all the samples in the fecal microbiome transplant study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  % TODO: Verify this
  The reason for this seems to derive from the mislabelling of constitutive taxa that are present in high abundance in the community, which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

  Figure \ref{fig:figure2}B is the PCA plot of all the generated co-occurrence networks, colored by the databases in the TA step (left) and the network inference algorihtms in the NI step (right).
  In other words, each point corresponds to a network generated using different combination of tools, and captures how much the final network is affected by such choice.
  The importance of the TA step indicated in Figure \ref{fig:figure2}A is also reflected here, in the fact that most of the networks can be clearly separated based on the database used (Figure \ref{fig:figure2}B).
  However, it is also evident that some of the networks, especially those inferred using the direct association based network infernce methods, are much closer in the PCA plot regardless of the reference database used.
  % TODO: Figure out the how the OP step plays a role in the PCA plot
  % TODO: Supplementary Figure S2
  It can also be seen that the dissimilarity between the networks decreases when the low abundance \ac{otu}s are removed from the network.
  These results suggest that the most important criterion for accurate comparative analyses of co-occurrence networks is the taxonomy reference database and the level of filtering of the taxonomy tables prior to network inference.

@@

  Denoising and clustering are commonly carried out to generate representative sequences from the demultiplexed and trimmed 16S sequencing data to obtain the \ac{otu}/\ac{esv} tables (counts of these representative sequences for each sample).
  In order to compare the representative sequence count tables generated by different tools we processed the same 16S sequencing reads (samples from a fecal microbiome transplant study~\cite{Kang2017}) using 5 different methods: open-reference clustering, closed-reference clustering, denovo clustering, \ac{dada2}~\cite{Callahan2016} and Deblur~\cite{Amir2017}.
  The first three methods are from the vsearch plugin and Deblur is from the deblur plugin of \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019}.
  The \ac{dada2} method is from the \ac{dada2} R package.

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  In both the comparisons, we set a count threshold of 10, such that if the count of the representative sequences in a particular sample is less than the threshold, it is omitted from the analysis.
  The values shown in the figures correspond to the mean UniFrac values across all samples in the study.
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A one can see that the representative sequences generated by the different methods, with the exception of Deblur, are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the assignment of sequences of low abundance.

  % TODO: Supplementary work - Figure S3
  In order to verify this claim, for each of these methods we use the \ac{gg} taxonomy database to assign taxonomies to the representative sequences.
  We then correlate the abundances of matching taxonomies between every pairwise combination of DC methods (Figure \ref{fig:figureS1}A and B).
  The \ac{esv} tables generated by methods that perform denoising are very similar to each other ($\sim0.91$) and the \ac{otu} tables generated by the clustering methods are very similar to each other ($\sim0.9$), but results of denoising and clustering are highly uncorrelated with each other ($\sim0.4$) (Figure \ref{fig:figureS1}C).

  % TODO: Update thresholds (10) on the mock datasets and check again
  These comparisons only elucidate the pairwise similarity or dissimilarity of a pair of methods.
  In order to determine the tool that most accurately recapitulates the reference sequences in the samples, we used the information about the known 16S sequences from the mock datasets.
  In particular, we used the pipeline to process mock community datasets using each of the possible methods included for this step.
  We next compared the predicted representative sequences with the expected representative sequences and their distribution.
  The results (Figure~\ref{fig:figure3}C and D) show that, for the mock datasets, the predicted sequence distributions are substantially different from the expected sequence distribution.
  This can be seen in the large values for both unweighted and weighted UniFrac distance values when compared to Figure~\ref{fig:figure3}A and B.
  This result is more exaggerated in the case of the unweighted UniFrac metric, where some of the datasets show a very high deviation from the expected sequences.
  These high deviations are primarily in one or two of the three datasets that were analyzed and show that the datasets themselves play a big role in the performance of these methods.
  Open-reference and denovo clustering methods perform the best under the weighted UniFrac metric and the worst under the unweighted UniFrac metric.
  This result can be attributed to the large number of low abundance representative sequences that are generated by these methods.
  Deblur performs poorly under weighted Unifrac and although its performance on the mock4 dataset is the best under unweighted UniFrac, its performance on the other datasets is average.
  There is no method that clearly outperforms the rest in all datasets.
  Based on their slightly better performance on the mock datasets, their \textit{de novo} error correcting nature and other previous studies~\cite{Nearing2018}, \ac{dada2} and Deblur seem to be in general the most reliable.
  Overall, since \ac{dada2} as compared to Deblur, displays better performance on all the mock datasets and under the weighted UniFrac metric, we have decided to recommend this tool for the DC step of the pipeline.

  % TODO: Supplementary work - Figure S4
  After the denoising, the sequences are subject to chimera checking.
  The \ac{micone} pipeline supports two different chimera checking methods, uchime and remove bimera.
  The uchime method is from \ac{qiime2}, whereas the remove bimera method is from the \ac{dada2} R package.
  We did not notice any significant difference between the two chimera checking methods, implying that they identify and remove mostly the same set of sequences as chimeras (Figure ???).

@@

  % How are the top assignments when compared
  % How does these assignments vary across level
  % What does this mean for us, conclusions
  % What does the mock data show?
  % Is there a best tool/database? What would you choose as the default?

  Taxonomy databases are used to assign taxonomic identities to the representative sequences obtained after the DC step.
  In order to compare the assigned taxonomies from different databases, we use the same reference sequences and assign taxonomies to them using different taxonomy reference databases.
  The three 16S taxonomic reference databases used in this study are SILVA~\cite{Quast2012}, \ac{gg}~\cite{DeSantis2006} and \ac{ncbi} RefSeq~\cite{Sayers2009}.
  SILVA and \ac{gg} are two popular 16S databases used for taxonomy identification.
  The \ac{ncbi} RefSeq nucleotide database contains 16S rRNA sequences as a part of two BioProjects - 33175 and 33317.
  The three databases vastly differ in terms of their last update status - \ac{gg} was last updated on May 2013, SILVA was last updated on August 2020 at the time of writing and \ac{ncbi} is updated regularly as new sequences are curated.
  Since updates to taxonomic classifications are frequent, these databases vary significantly in terms of taxonomy hierarchies including species names and phylogenetic relationships~\cite{Balvociute2017}.
  Assignment using a particular database also requires a query tool, we use the NaiveBayes classifier from \ac{qiime2} for the \ac{gg} and SILVA databases and the blast tool (also included as a \ac{qiime2} plugin) for the \ac{ncbi} database.
  These tools have been well quantified and optimized~\cite{bokulichOptimizingTaxonomicClassification2018}, hence, we make use of the default parameters in our analyses.

  The representative sequences obtained from the \ac{dada2} method (with remove bimera for chimera checking) in the DC step were used for taxonomic assignment using the three reference databases.
  Figure~\ref{fig:figure4}A depicts a flow diagram that shows how the top 50 representative sequences (sorted by abundance) are assigned a Genus according to the three different databases.
  We observe that the top 50 representative sequences are assigned to 17 Genus in \ac{gg}, 23 in SILVA and 17 in \ac{ncbi}, however the sequences that are assigned to a particular Genus vary significantly based on the taxonomy database.
  % TODO: Annotate Figure 4A with bacteria names
  We observe that not only does the assigned Genus composition vary significantly, but the percentage of unassigned representative sequences (pink) also differ.
  Even the most abundant representative sequence is assigned to an "unknown" Genus in two of the three databases (\ac{ncbi} and \ac{gg}).
  A representative sequence might be assigned an "unknown" Genus for one of two reasons: the first is if the taxonomy identifier associated with the sequence in the database did not contain a Genus; the second (more likely) reason is that the database contains multiple sequences that are very similar to the query (representative) sequence and the consensus algorithm (from \ac{qiime2}) is unable to assign one particular Genus at the required confidence.
  We also observe that other abundant Genus like Bacteroides and Escherichia are also assigned to different representative sequences.
  For example, the most abundant genus in the \ac{gg} taxonomy table was \textit{Escherichia} whereas in the SILVA taxonomy table it was \textit{Escherichia-Shigella}.
  Although these are minor differences, when comparing a large number of taxonomy composition tables these problems are hard to diagnose.

  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between the top 100 assignments (by abundance) from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<67\%$ similarity between any pair of databases.
  % TODO: Verify this
  The assignment between SILVA and the other two databases is significantly different ($40\%$ mismatch) even at the Phylum level, indicating that 40 of the top 100 assignments at the Phylum level in the SILVA database are different in SILVA.
  The \ac{gg} and \ac{ncbi} assignments are more similar compared to the other pairwise comparisons, mainly due to the poor performance of SIVLA at the Phylum level.
  However, the number of mismatches for taxonomy assignments beyond the Family level are very high ($>66\%$), implying that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.

  % TODO: Supplementary work - Figure S5
  The comparison of all assigned genera instead of the just the top 20 contains the same percentage of matches and mismatches, implying that there does not seem to exist a correlation between abundance and mismatch.
  This suggests that the most abundant sequences are not necessarily the ones that are consistently matched to the same taxonomies in the different reference databases.

  As in the previous section, the comparisons so far only indicate similarity or dissimilarity between methods.
  In order to obtain an absolute measure of accuracy of the taxonomic assignments we use the expected reference sequences from the mock datasets as the query sequences for the databases and the expected taxonomic composition as the standard to compare against (Figure~\ref{fig:figure4}C).
  Here, we observe that none of the databases perform better than the others in absolute terms and the dissimilarity is high, indicating that all the databases perform poorly when trying to recapture the expected taxonomic composition.

  Given that no database performs better than others against mock datasets, the choice of which database to use should be driven by other reasons.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth.
  % TODO: Find reference for this
  Since the \ac{gg} database is more widely used in the field~[ref], to enable easier comparison with published networks in literature, we set \ac{gg} as the \ac{micone} standard for taxonomy assignment.
  On the other hand, since the degree of similarity of assignments between \ac{ncbi} and \ac{gg} is fairly high, and due to its regular updation and maintenance the \ac{ncbi} database is also a good choice for the user.

  % TODO: More refs to support our argument?
 % There are also other studies, [ref, OTT paper] that focus on the database aspect and they too have found that...
